Data Visualisation in R

### 2023-11-01 inst/tutorials/MSc_Data_Vis/MSc_Data_Vis_v2.Rmd
new update to add exercise free tutorial

```{r Ex1, exercise = TRUE}
summary(lm(anscombe$y1 ~ anscombe$x1))
```

@@

```{r Ex3test, exercise = T}

library(palmerpenguins)

@@

# boxplot
boxplot(flipper_length_mm ~ species, data = penguins)

@@

```{r Ex4, exercise = T}
ggplot(penguins)
```

@@

```{r Ex5, exercise = T}
ggplot(penguins, aes(x = flipper_length_mm))
```

@@

```{r Ex7, exercise = T}
ggplot(penguins, aes(x = flipper_length_mm)) +
  geom_histogram() +
  labs(x = "Flipper Length (mm)", y = "Frequency", title = "Histogram of flipper length")
```

@@

```{r Ex8, exercise = T}
ggplot(penguins, aes(x = flipper_length_mm)) +
  geom_histogram(colour = "blue", fill = "lightblue")
```

@@

```{r Ex9, exercise = T}
ggplot(penguins, aes(x = flipper_length_mm)) +
  geom_histogram()
```

@@

```{r Ex10, exercise = T}
ggplot(penguins, aes(x = flipper_length_mm, fill = species)) +
  geom_histogram(colour = "black")
```

@@

```{r Ex11, exercise = T}
ggplot(penguins, aes(x = flipper_length_mm, fill = species)) +
  geom_density()

@@

```{r Ex12, exercise = T}
ggplot(penguins, aes(x = flipper_length_mm)) +
  geom_histogram() +
  facet_wrap(~species)

@@

```{r Ex13, exercise = T}

ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point()

@@

```{r Ex14, exercise = T}

ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point() +
  stat_smooth()

@@

```{r}
lm(bill_depth_mm ~ bill_length_mm, data = penguins)
```

@@

```{r Ex15, exercise = T}

ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point() +
  stat_smooth(method = "lm")

@@

```{r Ex16, exercise = T}

ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point() +
  stat_smooth(method = "lm")

@@

```{r Ex17, exercise = T}

ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point() +
  scale_colour_manual(values = c("blue", "red", "purple"))

@@

```{r Ex18, exercise = T}

ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point(alpha = 0.8)

@@

```{r Ex19, exercise = T}

ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point(alpha = 0.8, size = 3)

@@

```{r Ex20, exercise = T}

@@

```{r Ex21, exercise = T}

ggplot(penguins) +
  geom_point(aes(x = bill_length_mm, y = flipper_length_mm, colour = species))

@@

```{r Ex22, exercise = T}

@@

```{r Ex23, exercise = T}

ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_violin()

@@

```{r Ex24, exercise = T}

ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_violin() +
  geom_boxplot(notch = T)

@@

```{r Ex25, exercise = T}

ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_violin() +
  geom_boxplot(width = 0.4, notch = T)

@@

```{r Ex26, exercise = T}

ggplot(penguins, aes(x = species, y = flipper_length_mm, fill = species)) +
  geom_violin() +
  geom_boxplot(width = 0.4)

@@

```{r Ex27, exercise = T}

ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_violin(aes(fill = species)) +
  geom_boxplot(width = 0.4, fill = "grey90", notch = T)

@@

```{r Ex28, exercise = T}

ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_jitter()

@@

```{r Ex29, exercise = T}

ggplot(penguins, aes(x = species, y = flipper_length_mm, colour = species)) +
  geom_boxplot() + 
  geom_jitter(width = 0.3)

@@

```{r Ex30, exercise = T}

ggplot(penguins, aes(x = species, y = flipper_length_mm, colour = species)) +
  geom_boxplot() + 
  geom_jitter(width = 0.3, alpha = 0.3) +
  theme_bw()

>>>>

```{r}
summary(lm(anscombe$y1 ~ anscombe$x1))
```

@@

```{r eval = F}
library(palmerpenguins)

@@

# boxplot
boxplot(flipper_length_mm ~ species, data = penguins)
```

@@

```{r eval = F}
ggplot(penguins)
```

@@

```{r eval = F}
ggplot(penguins, aes(x = flipper_length_mm))
```

@@

```{r eval = F}
ggplot(penguins, aes(x = flipper_length_mm)) +
  geom_histogram() +
  labs(x = "Flipper Length (mm)", y = "Frequency", title = "Histogram of flipper length")
```

@@

```{r eval = F}
ggplot(penguins, aes(x = flipper_length_mm)) +
  geom_histogram(colour = "blue", fill = "lightblue")
```

@@

```{r eval = F}
ggplot(penguins, aes(x = flipper_length_mm)) +
  geom_histogram()
```

@@

```{r eval = F}
ggplot(penguins, aes(x = flipper_length_mm, fill = species)) +
  geom_histogram(colour = "black")
```

@@

```{r eval = F}
ggplot(penguins, aes(x = flipper_length_mm, fill = species)) +
  geom_density()

@@

```{r eval = F}
ggplot(penguins, aes(x = flipper_length_mm)) +
  geom_histogram() +
  facet_wrap(~species)

@@

```{r eval = F}
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point()

@@

```{r eval = F}
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point() +
  stat_smooth()

@@

```{r}
lm(bill_depth_mm ~ bill_length_mm, data = penguins)

@@

```{r eval = F}
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point() +
  stat_smooth(method = "lm")

@@

```{r eval = F}
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point() +
  stat_smooth(method = "lm")

@@

```{r eval = F}
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point() +
  scale_colour_manual(values = c("blue", "red", "purple"))

@@

```{r eval = F}
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point(alpha = 0.8)

@@

```{r eval = F}
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point(alpha = 0.8, size = 3)

@@

```{r eval = F}
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point() +
  scale_x_continuous(breaks = seq(35, 60, 5))

@@

```{r eval = F}
ggplot(penguins) +
  geom_point(aes(x = bill_length_mm, y = flipper_length_mm, colour = species))

@@

```{r eval = F}
ggplot(penguins, aes(x = flipper_length_mm, fill = species)) +
  geom_density(alpha = 0.5)

@@

```{r eval = F}
ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_violin()

@@

```{r eval = F}
ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_violin() +
  geom_boxplot(notch = T)

@@

```{r eval = F}
ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_violin() +
  geom_boxplot(width = 0.4, notch = T)

@@

```{r eval = F}
ggplot(penguins, aes(x = species, y = flipper_length_mm, fill = species)) +
  geom_violin() +
  geom_boxplot(width = 0.4)

@@

```{r eval = F}
ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_violin(aes(fill = species)) +
  geom_boxplot(width = 0.4, fill = "grey90", notch = T)

@@

```{r eval = F}
ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_jitter()

@@

```{r eval = F}
ggplot(penguins, aes(x = species, y = flipper_length_mm, colour = species)) +
  geom_boxplot() + 
  geom_jitter(width = 0.3)

@@

```{r eval = F}
ggplot(penguins, aes(x = species, y = flipper_length_mm, colour = species)) +
  geom_boxplot() + 
  geom_jitter(width = 0.3, alpha = 0.3) +
  theme_bw()

### 2023-11-01 inst/tutorials/MSc_Data_Vis/MSc_Data_Vis_v3.Rmd
new update to add exercise free tutorial

---
title: "Data Visualisation in R"
author: Dr Susan Johnston [Susan.Johnston@ed.ac.uk](mailto:Susan.Johnston@ed.ac.uk)
date: "1st November 2023"
output: learnr::tutorial
runtime: shiny_prerendered
description: Practical session on data visualisation with ggplot2. Demonstrator - Sarah Dobson.
---

>>>>

---
title: "Data Visualisation in R"
author: "Dr Susan Johnston [Susan.Johnston@ed.ac.uk](mailto:Susan.Johnston@ed.ac.uk)"
date: "1st November 2023"
output:
  pdf_document: default
  html_document: default
description: "Practical session on data visualisation with ggplot2. Demonstrator -
  Sarah Dobson."
---
